HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2022-01-11 hermes_paper/hermes_ieee.tex
remove the Accuracy formula (confusing) and minor changes

\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.} and Jean Bellot\thanks{Jean Bellot: Heuritech, France.}}
%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
%\thanks{M. Shell was with the Department
%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. the RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$ 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
$$
Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters. Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
$$
Our hybrid model forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
\begin{align}
\label{eq:nows:full:model}
\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} \\
&= \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
\end{align}

@@

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
  \caption{Temporal split for our training process}
\label{fig:train_eval_test_set}
\end{figure*}

\begin{figure}
  \centering
    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
  \caption{$\classifier$ and $\predictor$ architecture.}
\label{fig:rnn_architecture}
\end{figure}

@@

To compare the different methods, we use the Mean Absolute Scaled Error (MASE) for seasonal time series. As our sequences have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence and suited for our seasonal fashion time series. The MASE metric is defined as follows, with $m$ the seasonal period:
\begin{align*}
\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
\end{align*}
Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not. In a given year, an increasing trend is defined as a trend that does more than 5\% of growth on average with respect to the previous year. In the same way, a decreasing trend is defined as a trend that declines by 5\% on average or more. Other trends are classified as flat trends. With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends. On the {\em test} set, for each method, the accuracy is defined as follows:
\begin{align*}
\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
\end{align*}
where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.

@@

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
%  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{ACCURACY}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:metricresults}
\end{table}

@@

\begin{table}
  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset. The MASE average on all our time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed.}
  \centering
% \resizebox{0.85\textwidth}{!}{ 
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
%    \hline
	 \hline
	 &&& \\
     \textit{snaive} && 0.871 & - \\
     \textit{thetam}  && 0.849 & - \\
     \textit{arima} && 0.821 & - \\
     \textit{ets} && 0.801 & - \\
     \textit{stlm} && 0.765 & - \\
     \textit{lstm-nows} && 0.740 & 0.007 \\
     \textit{tbats} && 0.734 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
  \end{tabular}

@@

  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
%    \hline
	\hline
	 &&& \\
     \textit{snaive} && 0.876 & - \\
     \textit{thetam}  && 0.823 & - \\
     \textit{arima} && 0.814 & - \\
     \textit{ets} && 0.785 & - \\
     \textit{lstm-nows} && 0.767 & 0.045 \\
     \textit{stlm} && 0.742 & - \\
     \textit{tbats} && 0.745 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
  \end{tabular}
%  }
\label{tab:1000metricresults}
\end{table}

@@

\begin{table*}
  \caption{Results summary on the m4 weekly dataset. For each metric, the average on all our time series is computed. For approaches using a neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
 % \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:m4metricresults}
\end{table*}

@@

\begin{figure}
\centering
%\begin{subfigure}{1.\textwidth}
 % \centering
  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
 % \label{fig:m4parameter:sub1}
%\end{subfigure}
%\begin{subfigure}{1.\textwidth}
 % \centering
  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
  %\label{fig:m4parameter:sub2}
%\end{subfigure}
%\begin{subfigure}{1.\textwidth}
  %\centering
  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
  %\label{fig:m4parameter:sub3}
%\end{subfigure}
\caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate. For each parameter, 10 models with different seeds have been trained. The mean and the standard deviation are represented with a point and a vertical. (Top) result of the HERMES model depending on the number of windows provided per time series to the RNN corrector. (Middle) Result of the HERMES model depending on the size of the batch size. (Bottom) Result of the HERMES model depending on the learning rate of the optimizer.}
\label{fig:m4parameter}
\end{figure}

>>>>

\author{Etienne David\thanks{Etienne David: Heuritech, France.}, Jean Bellot\thanks{Jean Bellot: Heuritech, France.} and Sylvain Le Corff\thanks{Sylvain Le Corff:  Samovar, T\'el\'ecom SudParis, d\'epartement CITI, TIPIC, Institut Polytechnique de Paris, France.}}
%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
%\thanks{M. Shell was with the Department
%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. The RNN input is defined as the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$, $1\leqslant i \leqslant w$ and $k = i - h\lfloor \frac{i}{h} \rfloor$ 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+k|T}}{\meants^n_T}\,,\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
$$
Let $\rnn(.;\rnnparam)$ be the recurrent neural network model where $\rnnparam$ are  unknown parameters. Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
$$
Our hybrid model forecast is, for all $1\leqslant n \leqslant N$ and all $i \in \{1,\ldots,\lag\}$,
\begin{align}
\label{eq:nows:full:model}
\tspred^n_{T+i|T}  &= \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} \\
&= \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\,.\nonumber
\end{align}

@@

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{figure/train_eval_test_set}
  \caption{Temporal split for our training process. The three first years define our training set. The fourth year is used as our eval set and the final year is reserved for the test set.}
\label{fig:train_eval_test_set}
\end{figure*}

\begin{figure}
  \centering
    \includegraphics[width=0.8\linewidth]{figure/lstm_archi}
  \caption{Architecture of the RNN corrector part of the HERMES framework. The same architecture is used in the \textit{lstm} benchmark model.}
\label{fig:rnn_architecture}
\end{figure}

@@

To compare the different methods, we use the Mean Absolute Scaled Error (MASE) for seasonal time series. As our sequences have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence and suited for our seasonal fashion time series. The MASE metric is defined as follows, with $m$ the seasonal period:
\begin{align*}
\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
\end{align*}
Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not. In a given year, an increasing trend is defined as a trend that does more than 5\% of growth on average with respect to the previous year. In the same way, a decreasing trend is defined as a trend that declines by 5\% on average or more. Other trends are classified as flat trends. With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends.
%On the {\em test} set, for each method, the accuracy is defined as follows:
%\begin{align*}
%\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
%\end{align*}
%where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.

@@

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
%  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:metricresults}
\end{table}

@@

\begin{table}
  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset. The MASE average on all our time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed.}
  \centering
% \resizebox{0.85\textwidth}{!}{ 
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
%    \hline
	 \hline
	 &&& \\
     \textit{snaive} && 0.871 & - \\
     \textit{thetam}  && 0.849 & - \\
     \textit{arima} && 0.821 & - \\
     \textit{ets} && 0.801 & - \\
     \textit{stlm} && 0.765 & - \\
     \textit{lstm} && 0.740 & 0.007 \\
     \textit{tbats} && 0.734 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
  \end{tabular}

@@

  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
%    \hline
	\hline
	 &&& \\
     \textit{snaive} && 0.876 & - \\
     \textit{thetam}  && 0.823 & - \\
     \textit{arima} && 0.814 & - \\
     \textit{ets} && 0.785 & - \\
     \textit{lstm} && 0.767 & 0.045 \\
     \textit{stlm} && 0.742 & - \\
     \textit{tbats} && 0.745 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
  \end{tabular}
%  }
\label{tab:1000metricresults}
\end{table}

@@

\begin{table*}
  \caption{Results summary on the m4 weekly dataset. For each metric, the average on all our time series is computed. For approaches using a neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
 % \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
     \textit{S.Smyl} \cite{hyndman2020package} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
     \textit{\textbf{hermes-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:m4metricresults}
\end{table*}

@@

\begin{figure}
\centering
%\begin{subfigure}{1.\textwidth}
 % \centering
  \includegraphics[width=1.\linewidth]{figure/m4_nb_of_window}
  %\caption{result of the HERMES model on the M4 dataset model depending of the number of windows provided per time series to the RNN corrector}
 % \label{fig:m4parameter:sub1}
%\end{subfigure}
%\begin{subfigure}{1.\textwidth}
 % \centering
  \includegraphics[width=1.\linewidth]{figure/m4_batch_size}
  %\caption{result of the HERMES model on the M4 dataset model depending of the size of the batch size}
  %\label{fig:m4parameter:sub2}
%\end{subfigure}
%\begin{subfigure}{1.\textwidth}
  %\centering
  \includegraphics[width=1.\linewidth]{figure/m4_learning_rate}
  %\caption{result of the HERMES model on the M4 dataset model depending of learning rate of the optimizer}
  %\label{fig:m4parameter:sub3}
%\end{subfigure}
\caption{OWA for the \textit{hermes-tbats} model on the M4 weekly dataset depending on 3 parameters used during the RNN training: Number of moving windows per time series, the batch size and the learning rate. For each parameter, 10 models with different seeds have been trained. The mean and the standard deviation are represented with a point and a vertical. (Top) Result of the HERMES model depending on the number of windows provided per time series to the RNN corrector. (Middle) Result of the HERMES model depending on the size of the batch size. (Bottom) Result of the HERMES model depending on the learning rate of the optimizer.}
\label{fig:m4parameter}
\end{figure}
